---
lang: pt
vignette: >
  %\VignetteIndexEntry{Export ODK Collect}
  %\VignetteEngine{quarto::pdf}
  %\VignetteEncoding{UTF-8}
---


```{=latex}

\input{latex/capa.tex}
\clearpage
\tableofcontents
\clearpage

```

## Exportando os dados do `ODK Collect`

`readInstancesXML()`

 Extract data from ODK Collect instance XMLs (without ODK Briefcase)
 Reads all submission XMLs stored under an ODK Collect `instances/`
 directory and returns them as a named list of data frames (one per
 repeat level).

A função extrai os dados que estão em `instance/treeCensusForm_*.xml` para o diretório especificado no computador. São criados 7 arquivos `formBase-*.csv`, um para cada repetição de pergunta do formulário. Os arquivos `.csv` tem os nomes das instancias de repetição: `formBase`,`rep_cover`, `subquad`, `tree`, `sec_stem`, `miss`, `miss_sec_stem`.


```{r }

library(odkTreeCensus)

dataDir <- "/home/aao/Ale2026/AleProjetos/PPEIC/censo2026/dadosCampo2026/odkOut2026"
tabsDir <- dir(dataDir)
nTabs <- length(tabsDir)
iDir <- file.path(dataDir, tabsDir, "instances")
eDir <- "/home/aao/Ale2026/AleProjetos/PPEIC/censo2026/rawDataCSV"
mediaDir <- file.path(eDir, "media")

for(i in 1:nTabs)
{
    readInstancesXML(instancesDir = iDir[i], expDir = eDir, mediaOutDir = mediaDir, formBase = tabsDir[i], overwrite = TRUE)
}


readInstancesXML(instancesDir = instDir, expDir = eDir, mediaOutDir = mediaDir, formBase = base, overwrite = TRUE)


```


## Juntando os dados exportados

Reads the `CSV` files produced by \code{\link{readInstancesXML}}, links the
records through the \code{KEY} / \code{PARENT_KEY} columns, repeats the
parent fields at the child level and writes a set of flat CSV files ---
one row per lowest level record --- inside \code{expDir/rawData}.

Media files that live under a \code{media} folder (possibly with
sub-directories) are copied, flattened, into \code{expDir/media}.

`csvDir` Character. Directory that contains the CSV files exported by
  \code{readInstancesXML}.
`expDir` Character. Export directory where the merged files and the
  flattened \code{media} folder will be written. Defaults to \code{csvDir}.
`mediaDir` Character. Directory that containsultsults to \code{csvDir}.
`overwrite` Logical. Overwrite existing output files. Default
   \code{TRUE}.
   

```{r }



```
